%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% K-CV -- Klenske Curriculum Vitae
% 
% Simplified Friggeri CV 
% by Edgar Klenske (ed.klenske@gmx.de)
% https://github.com/eklenske/CV
%
% Forked from:
% Jelmer Tiente 
% https://github.com/JelmerT/CV
%
% Based on original work by:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{k-cv} % Add 'print' as an option into the square
                       % bracket to remove colors from this template
                       % for printing


\begin{document}
\header{Clara}{ Stafford}{PhD Candidate}{548-888-1993}{\href{https://clarastafford.netlify.app/}{clarastafford.netlify.app/}}{\href{mailto:clara.stafford922@gmail.com}{clara.stafford922@gmail.com}} % Your name and current job

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
%\section{date of birth}
%\color{gray}1993-05-18
%\section{contact}
%548-888-1993
%\href{mailto:clara.stafford922@gmail.com}{clara.stafford922@gmail.com}
%\href{https://clarastafford.netlify.app/}{clarastafford.netlify.app/}
\section{languages}
French native spoken, reading, and writing
~
English native spoken, reading, and writing
\section{programming}
R, MPlus, SPSS, JASP \& Python
\end{aside}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2017 \to now}
{Ph.D}
{Western University}
{Specialization in Quantitative Psychology}
%------------------------------------------------
\entry
{2015 \to 2017}
{Master {\normalfont of Science}}
{Western University}
{Specialization in Behavioural and Cognitive Psychology}
%------------------------------------------------
\entry
{2012 \to 2015}
{Bachelor {\normalfont of Arts}}
{McGill University}
{Specialization in Psychology}
%------------------------------------------------
\end{entrylist}

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{May 2021 \to now}
{Electronic Arts}
{Montréal, Québec, Canada}
{\emph{UX Research Co-Op} \\
Developed spreadsheets for risk analysis on exotic derivatives on a wide array 
of commodities (ags, oils, precious and base metals), managed blotter and 
secondary trades on structured notes, liaised with Middle Office, Sales and 
Structuring for bookkeeping. \\
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Nominted for the Learning Award by my team.
\end{itemize}}
%------------------------------------------------
\entry
{2018 \to 2020}
{Human Resource Systems Group Inc.}
{Ottawa, Ontario, Canada}
{\emph{Junior Social Sciences Research Analyst} \\
Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
\entry
{2019}
{Western University}
{London, Ontario, Canada}
{\emph{Programmer/Analyst} \\
Deparment of Statistics and Actuarial Sciences taught SPSS}
%------------------------------------------------
\entry
{2015 \to now}
{Western University}
{London, Ontario, Canada}
{\emph{Graduate Teaching Assistant} \\
Worked in the Nerd Herd and helped to solve computer problems by asking 
customers to turn their computers off and on again.}
%------------------------------------------------
\end{entrylist}

\clearpage

\smallheader{clara}{ stafford}

%-------------------------------------------------------------------------------
%	AWARDS SECTION
%-------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2021}
{rstudio::global(2021) Diversity Scholar}
{RStudio}
{Awarded to the top student in their final year of a Bachelors degree.}
%-----------------------------------------------
\entry
{2020}
{Adult Program Assistant of the Year}
{London Skating Club}
{Awarded to best adult PA of the year}
%------------------------------------------------
\entry
{2020}
{G. Keith Humphrey Memorial Award}
{Western University}
{Awarded to blah blah nominated by faculty}
%------------------------------------------------
\entry
{2019}
{Graduate Student Teaching Award}
{Western University}
{Awarded to blah blah nominated by students}
%------------------------------------------------
\entry
{2019-2020}
{Ontario Graduate Scholarship}
{Western University}
{Awarded to blah blah}
%------------------------------------------------
\entry
{2016}
{Reva Gerstein Fellowship for Masters Study in Psychology}
{Western University}
{Awarded to MSc students}
%-----------------------------------------------
\entry
{2016}
{George Hannah Global Opportunities Travel Award}
{Western University}
{Awarded to blah blah}
\end{entrylist}

%-------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%-------------------------------------------------------------------------------

\section{communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2019}
{Conference Poster}
{The American Academy of Neurology Sports Concussion Conference}
{\emph{The association between a history of self-reported concussion and response inhibition: a population-based study.}}
%------------------------------------------------
\entry
{2019}
{Conference Poster}
{Association for the Scientific Study of Consciousness}
{\emph{The neural basis of external responsiveness in prolonged disorders of consciousness.}}
%------------------------------------------------
\entry
{2018}
{Conference Poster}
{Rotman Research Institute Conference: TBI and Concussion}
{\emph{A large-scale investigation of the relationship between concussion and cognition in the general public.}}
%------------------------------------------------
\entry
{2016}
{Conference Poster}
{Society for Neuroscience}
{\emph{The relationship between overt responsiveness and white matter abnormalities in patients with disorders of consciousness.}}
%------------------------------------------------
\entry
{2016}
{Conference Poster}
{Canadian Association for Neuroscience}
{\emph{The role of thalamo-motor fibre damage in overt motor responses in disorders of consciousness.}}
%------------------------------------------------
\entry
{2016}
{Conference Poster}
{Lake Ontario Visionary Establishment}
{\emph{Mapping structural connectivity of thalamic nuclei at ultra-high fields.}}
%------------------------------------------------
\end{entrylist}

%-------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-------------------------------------------------------------------------------

\section{publications}
%\bibentry{title}{authors}{journal info}{doi}\\
%------------------------------------------------
\bibentry{Concussion related deficits in the general population predict impairments in varsity footballers.}{\textbf{Stafford, Clara A.}, Stojanoski, B., Wild, C. J., Brewer-Deluce, D., \& Owen, A. M.}{\emph{Journal of Neurology, 267}, 1970-1979, 2020}{\href{https://doi.org/10.1007/s00415-020-09749-9}{https://doi.org/10.1007/s00415-020-09749-9}}\\
%-------------------------------------------------
\bibentry{ The neural basis of external responsiveness in prolonged disorders of consciousness.}{\textbf{Stafford, Clara A.}, Owen, A. M., \& Fernandez-Espejo, D.}{\emph{NeuroImage: Clinical, 22}, 101791, 2019}{\href{https://doi.org/10.1016/j.nicl.2019.101791}{https://doi.org/10.1016/j.nicl.2019.101791}}

%\clearpage

%\smallheader{clara}{ stafford}

\end{document}
